COG-ED Manuscript

### 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
update mlm

@@

>>>>

  ## plot model fit of the final model ----
  plot_model(mfinal_h2b, type = "diag")

  # FIXME: do we want to include  a table like Table 3. in Westbrook et al.?
    # if we decide to include a table of mlm results, I propose to include a table with
    # term/parameter - Beta - SE - p-value - random effects (SD)

  # TODO: Corinna go on here :) 
    # -> get results for reporting
    # -> get means for plotting, plot results (if requested)
    # -> write methods
    # -> write results

  # TODO: it would be easy to integrate NFC as level 2 predictor into the analysis
    # to identify the personality influence on sv
    # it goes in the same direction as hypothesis 3a, but would hold some more information
    # a corresponding hypothesis could be
    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores" 
    # What do you think?

@@

### Changes in subjective values depend reliably on n-back level
